SAT Competition 2020\tnoteref{title}

### 2020-12-27 paper/main.tex
cloud

\begin{table}[t]
\smaller
\centering
\begin{tabular}{|l|l|l|}
\hline
\bf Team & \bf Solver & \bf Rank\\
\hline
Schreiber & mallob-mono & 1\\
\hline
\stack{Ehlers, Kulczynski, }{Nowotka, Sieweck}~ & TopoSAT2 & 2\\
\hline
Riveros & Slime & 3\\
\hline
\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}~ & Paracooba & -\\
& Paracooba-March & -\\
\hline
Hartung & CTSat & -\\
\hline
\end{tabular}
\caption{Teams and Solvers participating in the cloud track.}
\end{table}

@@

The massively parallel SAT solver Mallob is based on HordeSAT~\cite{}. 
Mallob is a framework for massivley parallel and distributed \emph{malleable job scheduling}, and thus can perform dynamic load balancing on many jobs of varying priorty.
However, in the submitted version Mallob Mono, this functionality is disabled, as traditionally in SAT Competition all resources are busy solving one single instance only.

Mallob uses the the 2018 version \emph{bcj} of Lingeling~\cite{} and employs diversification via randomized sparse initialization of branching scores just like it is done in Plingeling~\cite{}. 
Every 14th process, however, runs the local search solver YalSAT~\cite{}.

Clause exchange is handled considerably different from previous approach. 
Workers are organized in a binary tree and clauses are asynchronously aggregated in a buffer which is passed along this tree from leafs to the root. 
Each node performs a three way merge of the local and the two incoming buffers. 
Only the final aggragate at the root of that binary tree is broadcast to all the solvers.

To limit sharing, there is a global size limit of $5$ for all the shared clauses. 
The buffer has a limited size as well, but that size depends on the position in the binary tree, with root having the largest buffer and leaves the smallest. 
Clauses are sorted by there size during aggregation, such that smaller clauses are preferred over longer clauses. 
Duplicates are filtered out using a bloom filter, which is cleared periodically. 
There is a special filter for duplicate unit-clause which especially useful during startup.

@@

TopoSAT~2 is a massively parallel SAT solver using Glucose~3 with lockfree clause-exchange as in ManySAT~\cite{} on each node, and using MPI to share clauses between nodes.

In Toposat~2, diversification is done via different strategies used for branching, restarting and clause forgetting. 
Clauses are strengthened before they are exported. 
Locally, clause import is delayed until the local trail-size is low in a monitored period.

@@

Slime is build on top of MapleLCMDistChronoBT and was first submitted to SAT Race 2019 suggesting the new phase selection heuristic~\cite{}. 
The 2020 version apparently adds some kind of periodic randomization in geometrically increasing intervals~\cite{}. 
Even thought the sequential solver was unsuccessful in the Main Track, its MPI-based cloud version, won the third price in this competitions cloud track.

>>>>

\begin{table}[t]
\smaller
\centering
\begin{tabular}{|l|l|l|}
\hline
\bf Team & \bf Solver & \bf Rank\\
\hline
Schreiber & \solver{mallob-mono} & 1\\
\hline
\stack{Ehlers, Kulczynski, }{Nowotka, Sieweck}~ & \solver{TopoSAT2} & 2\\
\hline
Riveros & \solver{Slime} & 3\\
\hline
\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}~ & \solver{Paracooba} & -\\
& \solver{Paracooba-March} & -\\
\hline
Hartung & \solver{CTSat} & -\\
\hline
\end{tabular}
\caption{Teams and Solvers participating in the cloud track.}
\end{table}

@@

\solver{Mallob} is a fork of the generic massively parallel SAT solver \solver{HordeSAT}~\cite{Balyo:2015:HordeSAT}. 
\solver{Mallob} performs dynamic load balancing through \emph{malleable job scheduling} in case the input contains several SAT instances of varying priorty. 
This functionality is disabled in the submitted variant \solver{Mallob Mono}.

\solver{Mallob} mainly uses \solver{Lingeling-bcj} and diversifies via randomized sparse initialization of branching scores. 
However, as every 14th solver \solver{Mallob} spawns the SLS solver \solver{YalSAT}~\cite{Biere:2018:LingelingYalsat}.

\solver{Mallob} shares clauses by organizing solvers in a binary tree in which clauses are asynchronously aggregated in a buffer which is passed along this tree from leafs to the root. 
Each node performs a three-way merge of its local export and the two incoming buffers. 
The aggragate that approaches the root of the binary tree is then broadcast to all solvers~\cite{}.

\solver{Mallob} uses a global clause size limit and a dynamic limit for the sharing buffer, which depends on the position in the binary tree and grows while getting closer to the root. 
Clauses are sorted by their size during aggregation, such that smaller clauses are preferred over longer clauses. 
Duplicates are avoided by using a bloom filter which is periodically cleared~\cite{}.

@@

\solver{TopoSAT~2} is a massively parallel SAT solver build from \solver{Glucose~3}~\cite{Glucose3,Toposat2}. 
\solver{TopoSAT~2} uses lockfree clause-exchange for solvers running on the same maching, and MPI to share clauses between machines~\cite{ManySat,Proceedings}.

\solver{TopoSAT~2} strengthens clauses before export and delays clause import until the trail-size reaches a local minimum. 
\solver{Toposat~2} diversifies via the strategies used for branching, restarting and clause forgetting.

@@

\solver{Slime} is build from \solver{MapleLCMDistChronoBT} and was first submitted as a sequential solver to SAT Race~2019 with a new phase selection heuristic~\cite{SlimeSATRace2019}. 
The new submitted version of \solver{Slime} comes with periodic randomization in geometrically increasing intervals~\cite{}. 
Even thought its sequential version was unsuccessful in the Main track, the MPI-based cloud version of \solver{Slime} won the third price in the Cloud track.
